% - - - My Curriculum Vitae - - -

% Thanks to Thomas Jansson for template/class
% http://www.tjansson.dk/?p=604
% which originally came from here:
% http://linux.dsplabs.com.au/?p=54
% which itself was inspired by:
% http://www.biostat.harvard.edu/~paciorek/computingTips/computingTips.html

\documentclass[margin,line,a4paper]{resume}

\usepackage[usenames,dvipsnames]{color}
\usepackage[colorlinks]{hyperref}
% after this we set web links to blue and mail links to blue

\begin{document}
\name{\LARGE Nikolay Nikolov}

\begin{resume}

% - - - Contact - - -
\section{\mysidestyle Contact}

\hypersetup{urlcolor=RoyalBlue}
\href{mailto:nick@nklv.me}{nick@nklv.me} \hfill +44 7871 692188 \vspace{1mm}

% - - - Experience - - -
\section{\mysidestyle Employment}

\textbf{Goldman Sachs} \hfill London, United Kingdom \vspace{1mm} \\
\textsl{Summer Intern} \hfill 06.2015 - 08.2015 \vspace{2mm} \\
--- \\
Java (Dropwizard, Jersey); JavaScript (Angular, d3); MongoDB \\

\textbf{Variable Studio} \hfill London, United Kingdom \vspace{1mm} \\
\textsl{Part-time Developer} \hfill 10.2014 - 12.2014 \vspace{2mm} \\
--- \\
JavaScript (node.js); C++ (openFrameworks) \\

\textbf{Variable Studio} \hfill London, United Kingdom \vspace{1mm} \\
\textsl{Summer Intern} \hfill 7.2014 - 10.2014 \vspace{2mm} \\
--- \\
Research project (generative algorithms, WebGL); In-house open-source projects (WebGL, node.js, build tools) \\

\textbf{Setelis Labs} \hfill Sofia, Bulgaria \vspace{1mm} \\
\textsl{Summer Intern} \hfill 06.2012 - 7.2012 \vspace{2mm} \\
--- \\
iOS development with Facebook integration \\

% - - - Education - - -
\section{\mysidestyle Education}

\textbf{Goldsmiths College} \hfill London, United Kingdom\vspace{0.5mm}\\
\textsl{BSc Creative Computing } \hfill 2014 - 2016 \vspace{1mm} \\
(Direct entry to year 2)

\textbf{London College of Communication} \hfill London, United Kingdom\vspace{0.5mm}\\
\textsl{BA Sound Art } \hfill 2013 - 2014 \vspace{1mm} \\
(Incomplete)

\textbf{TSES High School} \hfill Sofia, Bulgaria \vspace{0.5mm} \\
\textsl{Computer Science Diploma} \hfill 2008 - 2013 \vspace{0.5mm} \\
6.00 / 6.00 Diploma thesis \\
5.17 / 6.00 Overall grade \\

% - - - Skills  - - -
\section{\mysidestyle Skills}
\textbf{Web} \\
JavaScript; HTML/CSS; WebGL; SQL

\textbf{Audio-visual} \\
C++; Java/Processing; Unity; Python

\textbf{iOS} \\
Objective-C

\textbf{Misc} \\
git; REST; UNIX

\newpage

\section{\mysidestyle Notable Projects}
\textbf{Chroma} 2015 \hfill
\href{http://chromaproject.co}{Project Website} --
\href{https://github.com/nicknikolov/chroma}{Github repository} \\
A Fashion design project with generative patterns implemented in WebGL. The concept was to create metallic fluid textures that you can interact with and create your own unique pattern which would be printed on a chosen model.
Under the hood, a Navier-Stokes shader implementation is projected into 3d space using flat a plane with a metal texture and z-tranform based on user interaction.

\textbf{Semicolon} 2015 \hfill
\href{https://github.com/nicknikolov/semicolon}{Github repository} \\
My group project during my second year at university involved creating a mobile IDE for the Processing programming language. I combined the open-source JavaScript-based editor Codermirror with the Processing-to-JS compiler by John Resig and added a number of touch and gesture-based features to create a nicer coding experience on a mobile device.

\textbf{London Music Hackday Winner} 2014 \hfill
\href{https://github.com/whg/spotijay}{Github repository} \\
Together with Will Gallia, I developed a web application that can beatmatch tracks provided by Spotify and create a continuous mix by choosing appropriate music by itself. That was made possible by using the Echonest API which provided the beats per minute and transient data. We were awarded the Echonest prize - a Spotify premium account for a year.

\textbf{Sapporter} 2014 \\
I was the programmer in this self-initiated project by friends. I created a iOS application and a node.js back-end server managing a Postgres database and talking to an Amazon S3 instance. The idea was to create a way for football fans to find out about interesting football games nearby (under-21s, friendlies, women's games etc.).
The application would provide travel and price guides.

\textbf{shufflr} 2013 \\
My high school diploma project was to develop an iOS application that would query your liked bands and musicians from your Facebook account and provide a custom-tailored news feed using RSS data from various music news sites.
The server was implemented using Ruby on Rails. \\

\section{\mysidestyle Activities}

\textbf{Goldsmiths} \\
Hacksmiths Society Member

\textbf{High School} \\
C programming curriculum; Games programming intro course

\textbf{Other} \\
I have attended various \href{http://www.meetup.com/HNLondon/}{meet-ups} and conferences for \href{http://www.startupschool.org/}{start-ups}, \href{https://en.wikipedia.org/wiki/Digitalk}{technology} and \href{http://www.alpha-ville.co.uk/exchange/}{digital art and design} in London and Sofia. \\
I have been involved in producing and performing \href{https://soundcloud.com/nick-nikolov}{electronic music} for several years.

\end{resume}
\end{document}
